Forecasting the United States 2024 Presidential Election

### 2024-11-04 paper/paper.qmd

In an ideal world, where a $100k in funds and all necessary resources could be obtained from a neutral source for the purpose of polling the population, the idealized methodology for a survey that aims to forecast the results of the US election should be one that uses quota sampling and the probability proportionate to size method to target the states of interest specifically. Historically, certain states have very strong and consistent party preferences; for example, we can be almost entirely certain even without conducting any current research that California would be voting Democrat, simply because this has been how they voted in the past eight elections [@blueredstate]. Out of the 51 states, there are 20 states which voted for the same party each time in the past nine elections and therefore there is a high probability that the pattern will be upheld with this year's election [@blueredstate]. On the other end of the spectrum, there are seven states which have voted for each party three of more times within the last nine elections—these would be the states of greater interest to us [@blueredstate].

@@

>>>>

In an ideal world, where a $100k in funds and all necessary resources could be obtained from a neutral source for the purpose of polling the population, the idealized methodology for a survey that aims to forecast the results of the US election should be one that uses quota sampling and the probability proportionate to size method to target the states of interest specifically. Historically, certain states have very strong and consistent party preferences; for example, we can be almost entirely certain even without conducting any current research that California would be voting Democrat, simply because this has been how they voted in the past nine elections [@blueredstate]. Out of the 51 states, there are 43 states which have voted for the same party seven or more times and therefore there is a high probability that the pattern will be upheld with this year's election [@blueredstate].

On the other end of the spectrum, there are seven states which have voted for each party three of more times within the last nine elections—these would be the states of greater interest to us [@blueredstate].

@@

=======
>>>>>>> 3831a5556d47b44b38240855a1f7d590aa816a2d
\newpage
